### 2020-08-27 transient.tex

This chapter discusses Moltres transient multiphysics simulations of the
\gls{MSFR} in four accident scenarios. These scenarios, adapted from the
\gls{MSFR} transient analyses with the Polimi and TUDelft models
\cite{fiorina_modelling_2014}, include unprotected reactivity
insertion, loss of heat sink, loss of flow, and pump overspeed accidents. The
term ``unprotected'' signifies accident scenarios without treactor SCRAM. As
such, these simulations provide an insight on the
\gls{MSFR}'s passive safety capabilities in the absence
of active safety systems. This work used the steady-state configuration
presented in the previous chapter as the initial conditions for the transient
simulations discussed in this chapter. Specifically, all steady-state spatial
values for neutron flux, delayed neutron precursor concentration, temperature,
velocity, and pressure were imported as the initial state of the transient
scenarios.

As noted by Fiorina et al. \cite{fiorina_modelling_2014}, explicit decay heat
modeling has a negligible effect in reactivity-, and pump-initiated
transients. Furthermore, only their Polimi model had this capability.
Therefore, they featured decay heat modeling for the loss of heat sink
accident scenario only. The current work also ran all transient simulations
without the decay heat model for a fair comparison. The only exception is the
loss of heat sink scenario in which two separate simulations with and without
the decay heat model were run. This work imposed simplifying assumptions in
our transient models to match the implementations in
\cite{fiorina_modelling_2014} as closely as possible, within Moltres'
capabilities. The details of the setup for each
transient simulation appear in the following sections.

@@

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.7\textwidth]{50pcm-jump}
    \caption{Power output during the prompt response following a 50 pcm
    step-wise unprotected reactivity insertion in the Moltres, Polimi, and
    TUDelft models \cite{fiorina_modelling_2014}.}
    \label{fig:50pcmjump}
\end{figure}

@@

Figure \ref{fig:50pcmjump} shows the rise in power output during
the initial prompt response. The prompt
response raises the power output to 4 GW by $t=0.001$ s.
Figures \ref{fig:50pcmheat} and \ref{fig:50pcmtemp} show the power output and
average core temperature increase beyond $t=0.001$ s following the 50 pcm
step-wise reactivity insertion in the Moltres, Polimi, and TUDelft models.
Power continues to rise at a slower rate up to 4.63 GW at around $t=0.005$ s,
at which point the negative reactivity from the Doppler effect and salt
expansion becomes greater
than the initial +50 pcm insertion. Power continues to fall as the average
core temperature rises. A slight change in slope occurs at $t=0.3$ s. The
elapsed time approximately corresponds to the average half-life of the two
shortest-lived delayed neutron precursor (DNP) groups ($t_{1/2}=0.195$ s and
$0.424$ s); the decay of the surplus precursors produced in the initial phase
negates a fraction of the negative reactivity from the elevated core
temperature. By $t=3$ s, most of the heated salt and \glspl{DNP} from the
initial phase will have circulated around the primary loop and returned to the
core. The heated salt causes a small, noticeable dip in power before the power
output stabilizes.

@@

Figure \ref{fig:polimidecaytemp} shows the loop-averaged temperature
increase in the Moltres and Polimi models \cite{fiorina_modelling_2014}. The
TUDelft model does not have a decay heat modeling capability. The Moltres
model predicts the same increasing trend in the temperature. The loop-averaged
temperature rises significantly at the start of the transient and continues to
rise at a decreasing rate. The loop-averaged temperature increase in the
Moltres model at $t=120$ s is approximately 17 K lower than that in the Polimi
model. It is difficult to ascertain the exact cause for this difference
without the power profile from the Polimi model with decay heat to compare
with. However, if the decay power output were similar, the stronger negative
temperature reactivity coefficient would cause the prompt power output in the
Moltres model to fall faster than the Polimi model. Consequently, the
loop-averaged temperature would be lower as shown in the figure. Overall, the
results for the loss of heat sink transient agree with the Polimi and TUDelft
model results in both cases, with and without decay heat modeling.

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.85\textwidth]{moltres-decay-power}
    \caption{Power output during
    an unprotected loss of heat sink transient in the Moltres model with and
    without decay heat.}
    \label{fig:moltresdecaypower}
    \includegraphics[width=.85\textwidth]{moltres-decay-temp}
    \caption{Average core temperature increase during
    an unprotected loss of heat sink transient in the Moltres model with and
    without decay heat.}
    \label{fig:moltresdecaytemp}
\end{figure}

@@

Pump overspeed refers to a sustained
increase in pump speed in the primary coolant loop. The increased flow rate
$\dot{m}$ impacts reactor performance in several ways.
It affects the neutronics by reducing the in-core $\beta$ as more of the
shorter-lived precursors will tend to flow out of the core before decaying.
This net loss of neutrons reduces the reactivity in the core, thereby causing
core temperatures to fall to counteract this change through temperature
reactivity feedback. The increased $\dot{V}$ also enhances the heat transfer
coefficient on the primary loop side of the heat exchanger and enables the
reactor to operate at a higher power output. At the same time, the improved
mixing flattens the temperature distribution in the core.

@@

Setting the exact dependence between the heat transfer coefficient $h$ and
$\dot{V}$ was problematic because
the pointwise heat exchanger implementation in Moltres performs differently
compared with the heat exchangers of finite volume in the Polimi and TUDelft
models \cite{fiorina_modelling_2014}. In a heat exchanger of finite volume,
most of the cooling occurs in the first half of the heat exchanger where the
temperature differential between the primary and intermediate loops is the
largest. In the Polimi and TUDelft models, the overall $h$ is a
harmonic mean of the $h_i$ on each side of the heat exchanger, given as:
%
\begin{align}
    h &= \frac{2}{\frac{1}{h_1} + \frac{1}{h_2}}, \\
    \intertext{where}
    h &= \text{overall heat transfer coefficient
    [W$\cdot$K$^{-1}$],} \nonumber \\
    h_1 &= \text{heat transfer coefficient on the primary loop side
    [W$\cdot$K$^{-1}$],} \nonumber \\
    h_2 &= \text{heat transfer coefficient on the intermediate loop side
    [W$\cdot$K$^{-1}$].} \nonumber
\end{align}
%
In addition to this, the Polimi and TUDelft models used the Dittus-Boelter
correlation \cite{dittus_heat_1930} for the relationship between $h_1$ and
$\dot{V}$. The Dittus-Boelter correlation for fluids being cooled is:
%
\begin{align}
    Nu &= 0.023 Re^{0.8} Pr^{0.3}, \label{eq:db} \\
    \intertext{where}
    Nu &= \text{Nusselt number} =
    \frac{\text{convective heat transfer}}{\text{conductive heat transfer}}
    = \frac{hL}{k}, \nonumber \\
    Re &= \text{Reynolds number} =
    \frac{\text{inertial forces}}{\text{viscous forces}} =
    \frac{\rho u L}{\mu}, \nonumber \\
    Pr &= \text{Prandtl number} =
    \frac{\text{momentum diffusivity}}{\text{thermal diffusivity}} =
    \frac{c_p \mu}{k}. \nonumber
\end{align}
%
The only direct relation to $\dot{V}$ in the Dittus-Boelter correlation is
through the Reynolds number, $Re$, which is directly proportional to
flow velocity $v$. This gives the following relation between $h$ and $v$:
%
\begin{align}
    h &\propto v^{0.8} \label{eq:hv} \\
    h &= \text{heat transfer coefficient [W$\cdot$K$^{-1}$],} \nonumber \\
    v &= \text{flow velocity [m$\cdot$s$^{-1}$].} \nonumber
\end{align}
%
However, this relation provided very different results in the unprotected pump
overspeed and loss of flow transients compared with the Polimi and TUDelft
models. This approach underpredicted the equilibrium power output in the
unprotected pump overspeed transient and overpredicted the same parameter in
the unprotected loss of flow transient. Upon further investigation, I
found that raising the power of $v$ from 0.8 to 1.1 brought the
average core temperatures closer to the results from the other models in both
transients. Therefore, this work adopted the raised power in this thesis.

Figures \ref{fig:poheat} and
\ref{fig:potemp} show the power output and average core temperature increase
during the unprotected pump overspeed transient in the Moltres, Polimi, and
TUDelft models. Figure \ref{fig:poshort} shows the same results for the first
20 seconds of the transient. At the start of the transient, the rising flow
rate cools the core and causes power output to rise sharply. Although the
average core temperature has a strictly decreasing trend, the temperature at
the center of the core briefly rises due to the sharp increase in power
output. Since this is the region where most of the fissions take place, the
Doppler effect and salt expansion causes the power output to stall and dip
briefly before rising again at $t=2.5$ s. The reactor tends to a new
equilibrium power output and average core temperature. The temperature
distribution in the core is more evenly distributed because the turbulent
thermal conductivity $k_t$ is directly proportional to $mu_t$.

@@

A loss of forced flow transient can occur in the event of a station blackout
without reactor SCRAM; the pumps would cease operating due to the loss of AC
electrical
power. Natural circulation resulting from temperature-dependent density
changes becomes the dominant driving force for salt flow in the primary loop.
Fiorina et al. \cite{fiorina_modelling_2014} applied the Boussinesq
approximation for buoyancy-driven flow in the Polimi and TUDelft models, but
this approach was not possible in Moltres because the primary loop is
partitioned into two separate geometries and used Dirichlet boundary
conditions at the inlet to drive flow. The Polimi and TUDelft
models featured complete exponential coast-downs of the pumps with a time
constant of 5 s. The final flow rate $\dot{V}_f$ from natural circulation
was approximately 18 times smaller than the initial $\dot{V}_0$. Figure
\ref{fig:flowrate} shows that the actual $\dot{V}$ decreased with a time
constant of 8 s. Thus, for the \gls{MSFR} model in Moltres, this work imposed
a similar exponential decay term with a time constant of 8 s on the inflow
Dirichlet boundary condition:
%
\begin{align}
    \dot{V} &= \dot{V}_f + (\dot{V}_0-\dot{V}_f) e^{-t/8},
    \label{eq:flowrate} \\
    \intertext{where}
    \dot{V}_f &= \text{final volumetric flow rate} = 0.25862
    \text{ m$^3\cdot$s$^{-1}$,} \nonumber \\
    \dot{V}_0 &= \text{initial volumetric flow rate} = 4.5
    \text{ m$^3\cdot$s$^{-1}$.} \nonumber
\end{align}
%
\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.6\textwidth]{lof-flow-rate}
    \caption{The change in flow rate in the Polimi and TUDelft models and the
    imposed flow rate in Moltres.}
    \label{fig:flowrate}
\end{figure}
%
The reduced $\dot{V}$ also decreases the heat transfer rate between the
primary and intermediate loop through the heat exchanger as the heat transfer
coefficient $h$ is dependent on the $\dot{V}$. For this loss of flow
transient, Fiorina et al. \cite{fiorina_modelling_2014} intended to focus
on the primary loop and assumed that only the pumps in the primary loop
failed.

An issue arose pertaining to the turbulent viscosity $\mu_t$ as a function of
$v$. When using this simple approximation, in which $\mu_t$ being directly
proportional
to $v$, the results from Moltres differed significantly compared with the
Polimi and TUDelft models. The difference is due to buoyancy-driven flow
contributing to turbulence; the turbulent energy $k$ equation in COMSOL's
$k$-$\epsilon$ model has an explicit source term from buoyancy effects
\cite{comsol_ab_comsol_2018}. Another point to note is the
Reynolds number remains constant if $\mu$ and $v$ decrease in tandem. This
preserves the existence of the recirculation zone in the core and it is at
odds with the results from the Polimi and TUDelft models, which show that the
recirculation zones disappear during the loss of flow transient. The current
work circumvented this issue by letting fixed fractions of the initial
$\mu_{t,0}$ be conserved regardless of the final flow velocity, according to
the following equation:
%
\begin{align}
    \mu_t &= \mu_c + (\mu_{t,0} - \mu_c) e^{-t/8} \label{lofmu} \\
    \intertext{where}
    \mu_c &= \text{ conserved fraction of $\mu_{t,0}$ [Pa$\cdot$s].} \nonumber
\end{align}
%
This measure allowed for laminar flow to develop in the core and yielded
results showing better qualitative agreement with those from the Polimi and
TUDelft models. The subsequent paragraphs discuss these results.

Figures \ref{fig:lofheat} and \ref{fig:loftemp} show the power output and
average core temperature increase during the unprotected loss of flow
transient in the Moltres, Polimi, and TUDelft models without decay heat
modeling. The three sets of results from Moltres correspond to $\mu_c =
\frac{1}{4} \mu_{t,0}, \frac{1}{2} \mu_{t,0}, \text{and } \frac{3}{4}
\mu_{t,0}$.
Although Moltres shows the same decreasing trend in power output, it failed to
capture the exact individual features in the reactor response. In the Polimi 
and TUDelft models, Fiorina et al. \cite{fiorina_modelling_2014}
stated that after around $t=15$ s, the ``flow pattern changed in the core and
the recirculation zones started to disappear''. The pocket of hot salt leaves
the core and causes a sudden drop in the average core temperature. In Moltres,
the wider peak in the average core temperature
indicates that there was a more gradual change in the flow pattern.

>>>>

This chapter discusses Moltres transient multiphysics simulations of the
\gls{MSFR} in four accident scenarios. These scenarios, adapted from the
\gls{MSFR} transient analyses with the Polimi and TUDelft models
\cite{fiorina_modelling_2014}, include unprotected reactivity
insertion, loss of heat sink, loss of flow, and pump overspeed accidents. The
term ``unprotected'' signifies accident scenarios without reactor SCRAM. As
such, these simulations provide an insight on the
\gls{MSFR}'s passive safety capabilities in the absence
of active safety systems. This work used the steady-state configuration
presented in the previous chapter as the initial conditions for the transient
simulations discussed in this chapter. Specifically, all steady-state spatial
values for neutron flux, delayed neutron precursor concentration, temperature,
velocity, and pressure were imported as the initial state of the transient
scenarios.

As noted by Fiorina et al. \cite{fiorina_modelling_2014}, explicit decay heat
modeling has a negligible effect in reactivity-, and pump-initiated
transients. Furthermore, only their Polimi model had this capability.
Therefore, they included decay heat modeling for the loss of heat sink
accident scenario only. The current work also ran all transient simulations
without the decay heat model for a fair comparison. The only exception is the
loss of heat sink scenario in which two separate simulations with and without
the decay heat model were run. This work imposed simplifying assumptions in
our transient models to match the implementations in
\cite{fiorina_modelling_2014} as closely as possible, within Moltres'
capabilities. The details of the setup for each
transient simulation appear in the following sections.

@@

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.7\textwidth]{50pcm-jump}
    \caption{Power output during the prompt response following a 50 pcm
    step-wise unprotected reactivity insertion in the Moltres model.}
    \label{fig:50pcmjump}
\end{figure}

@@

Figure \ref{fig:50pcmjump} shows the rise in power output during
the initial prompt response. The prompt
response raises the power output to 4 GW by $t=0.001$ s.
Figures \ref{fig:50pcmheat} and \ref{fig:50pcmtemp} show the power output and
average core temperature increase beyond $t=0.001$ s following the 50 pcm
step-wise reactivity insertion in the Moltres, Polimi, and TUDelft models.
Power continues to rise at a slower rate up to 4.63 GW at around $t=0.005$ s,
at which point the negative reactivity from the Doppler effect and salt
expansion becomes greater
than the initial +50 pcm insertion. Power continues to fall as the average
core temperature rises. A slight change in slope occurs at $t=0.3$ s. The
elapsed time approximately corresponds to the average half-life of the two
shortest-lived delayed neutron precursor (DNP) groups ($t_{1/2}=0.195$ s and
$0.424$ s); the decay of the surplus precursors produced in the initial phase
negates a fraction of the negative reactivity from the elevated core
temperature. By $t=3$ s, most of the heated salt and \glspl{DNP} from the
initial phase will have circulated the primary loop and returned to the
core. The heated salt causes a small, noticeable dip in power before the power
output stabilizes.

@@

Figure \ref{fig:polimidecaytemp} shows the loop-averaged temperature
increase in the Moltres and Polimi models \cite{fiorina_modelling_2014}. The
TUDelft model does not have a decay heat modeling capability. The Moltres
model predicts the same increasing trend in the temperature. The loop-averaged
temperature rises significantly at the start of the transient and continues to
rise at a decreasing rate. The loop-averaged temperature increase in the
Moltres model at $t=120$ s is approximately 17 K lower than that in the Polimi
model. Unfortunately, the power profile from the Polimi model is not available
for direct comparison.
However, if the decay power output were similar, the stronger negative
temperature reactivity coefficient would cause the prompt power output in the
Moltres model to fall faster than the Polimi model. Consequently, the
loop-averaged temperature would be lower as shown in the figure. Overall, the
results for the loss of heat sink transient agree with the Polimi and TUDelft
model results in both cases, with and without decay heat modeling.

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.85\textwidth]{moltres-decay-power}
    \caption{Power output during
    an unprotected loss of heat sink transient in the Moltres model with
    decay heat.}
    \label{fig:moltresdecaypower}
    \includegraphics[width=.85\textwidth]{moltres-decay-temp}
    \caption{Average core temperature increase during
    an unprotected loss of heat sink transient in the Moltres model with and
    without decay heat.}
    \label{fig:moltresdecaytemp}
\end{figure}

@@

Pump overspeed refers to a sustained
increase in pump speed in the primary coolant loop. The increased flow rate
$\dot{V}$ impacts reactor performance in several ways. It reduces the in-core
$\beta$ as more of the shorter-lived precursors will tend to flow out of the
core and decay in the subcritical outer loop region.
The increased $\dot{V}$ also enhances the heat transfer
coefficient on the primary loop side of the heat exchanger and introduces
cooler fuel salt to the core. The reactivity increase from the temperature
reactivity feedback outweighs the reactivity decrease from the loss of delayed
neutrons. Thus, the overall neutron flux and power output is higher at the
new equilibrium state. At the same time, the improved
mixing flattens the temperature distribution in the core.

@@

Setting the exact dependence between the heat transfer coefficient $h$ and
$\dot{V}$ was problematic because
the pointwise heat exchanger implementation in Moltres performs differently
compared with the heat exchangers of finite volume in the Polimi and TUDelft
models \cite{fiorina_modelling_2014}. In a heat exchanger of finite volume,
most of the cooling occurs in the first half of the heat exchanger where the
temperature differential between the primary and intermediate loops is the
largest. In the Polimi and TUDelft models, the overall $h$ is a
harmonic mean of the $h_i$ on each side of the heat exchanger, given as:
%
\begin{align}
    h &= \frac{2}{\frac{1}{h_1} + \frac{1}{h_2}}, \\
    \intertext{where}
    h &= \text{overall heat transfer coefficient
    [W$\cdot$K$^{-1}$],} \nonumber \\
    h_1 &= \text{heat transfer coefficient on the primary loop side
    [W$\cdot$K$^{-1}$],} \nonumber \\
    h_2 &= \text{heat transfer coefficient on the intermediate loop side
    [W$\cdot$K$^{-1}$].} \nonumber
\end{align}
%
In addition to this, the Polimi and TUDelft models used the Dittus-Boelter
correlation \cite{dittus_heat_1930} for the relationship between $h_1$ and
$\dot{V}$. The Dittus-Boelter correlation for fluids being cooled is:
%
\begin{align}
    Nu &= 0.023 Re^{0.8} Pr^{0.3}, \label{eq:db} \\
    \intertext{where}
    Nu &= \text{Nusselt number} =
    \frac{\text{convective heat transfer}}{\text{conductive heat transfer}}
    = \frac{hL}{k}, \nonumber \\
    Re &= \text{Reynolds number} =
    \frac{\text{inertial forces}}{\text{viscous forces}} =
    \frac{\rho u L}{\mu}, \nonumber \\
    Pr &= \text{Prandtl number} =
    \frac{\text{momentum diffusivity}}{\text{thermal diffusivity}} =
    \frac{c_p \mu}{k}. \nonumber
\end{align}
%
The only direct relation to $\dot{V}$ in the Dittus-Boelter correlation is
through the Reynolds number, $Re$, which is directly proportional to
flow velocity $v$. This gives the following relation between $h$ and $v$:
%
\begin{align}
    h &\propto v^{0.8} \label{eq:hv} \\
    h &= \text{heat transfer coefficient [W$\cdot$K$^{-1}$],} \nonumber \\
    v &= \text{flow velocity [m$\cdot$s$^{-1}$].} \nonumber
\end{align}
%
However, this relation provided very different results in the unprotected pump
overspeed and loss of flow transients compared with the Polimi and TUDelft
models. This approach underpredicted the equilibrium power output in the
unprotected pump overspeed transient and overpredicted the same parameter in
the unprotected loss of flow transient. Upon further investigation, it was
found that raising the power of $v$ from 0.8 to 1.1 brought the
average core temperatures closer to the results from the other models in both
transients. Therefore, this work adopted the raised power in this thesis.

Figures \ref{fig:poheat} and
\ref{fig:potemp} show the power output and average core temperature increase
during the unprotected pump overspeed transient in the Moltres, Polimi, and
TUDelft models. Figure \ref{fig:poshort} shows the same results for the first
20 seconds of the transient. At the start of the transient, the rising flow
rate cools the core by convecting heat away from the center and causes power
output to rise sharply. Although the
average core temperature has a strictly decreasing trend, the temperature at
the center of the core briefly rises due to the sharp increase in power
output. Since this is the region where most of the fissions take place, the
Doppler effect and salt expansion causes the power output to stall and dip
briefly before rising again at $t=2.5$ s. The reactor tends to a new
equilibrium power output and average core temperature. The temperature
distribution in the core is more evenly distributed because the turbulent
thermal conductivity $k_t$ is directly proportional to $\mu_t$.

@@

A loss of forced flow transient can occur in the event of a station blackout
without reactor SCRAM; the pumps would cease operating due to the loss of AC
electrical
power. Natural circulation resulting from temperature-dependent density
changes becomes the dominant driving force for salt flow in the primary loop.
Fiorina et al. \cite{fiorina_modelling_2014} applied the Boussinesq
approximation for buoyancy-driven flow in the Polimi and TUDelft models, but
this approach was not possible in Moltres because the primary loop is
partitioned into two separate geometries and uses Dirichlet boundary
conditions at the inlet to drive flow. The Polimi and TUDelft
models featured complete exponential coast-downs of the pumps with a time
constant of 5 s. The final flow rate $\dot{V}_f$ from natural circulation
was approximately 18 times smaller than the initial $\dot{V}_0$. Figure
\ref{fig:flowrate} shows that the actual $\dot{V}$ decreased with a time
constant of 8 s. Thus, for the \gls{MSFR} model in Moltres, this work imposed
a similar exponential decay term with a time constant of 8 s on the inflow
Dirichlet boundary condition:
%
\begin{align}
    \dot{V} &= \dot{V}_f + (\dot{V}_0-\dot{V}_f) e^{-t/8},
    \label{eq:flowrate} \\
    \intertext{where}
    \dot{V}_f &= \text{final volumetric flow rate} = 0.25862
    \text{ m$^3\cdot$s$^{-1}$,} \nonumber \\
    \dot{V}_0 &= \text{initial volumetric flow rate} = 4.5
    \text{ m$^3\cdot$s$^{-1}$.} \nonumber
\end{align}
%
\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.6\textwidth]{lof-flow-rate}
    \caption{The change in flow rate in the Polimi and TUDelft models and the
    imposed flow rate in Moltres.}
    \label{fig:flowrate}
\end{figure}
%
The reduced $\dot{V}$ also decreases the heat transfer rate between the
primary and intermediate loop through the heat exchanger as the heat transfer
coefficient $h$ is dependent on the $\dot{V}$. For this loss of flow
transient, Fiorina et al. \cite{fiorina_modelling_2014} intended to focus
on the primary loop and assumed that only the pumps in the primary loop
failed.

An issue arose pertaining to the turbulent viscosity $\mu_t$ as a function of
$v$. This simple approximation, in which $\mu_t$ being directly proportional
to $v$, causes the results from Moltres to differ significantly compared with
the Polimi and TUDelft models. The difference is due to buoyancy-driven flow
contributing to turbulence; the turbulent energy $k$ equation in COMSOL's
$k$-$\epsilon$ model has an explicit source term from buoyancy effects
\cite{comsol_ab_comsol_2018}. Another point to note is the
Reynolds number remains constant if $\mu$ and $v$ decrease in tandem. This
preserves the existence of the recirculation zone in the core and it is at
odds with the results from the Polimi and TUDelft models, which show that the
recirculation zones disappear during the loss of flow transient. The current
work circumvented this issue by retaining fixed fractions of the initial
$\mu_{t,0}$ regardless of the final flow velocity, according to
the following equation:
%
\begin{align}
    \mu_t &= \mu_c + (\mu_{t,0} - \mu_c) e^{-t/8} \label{lofmu} \\
    \intertext{where}
    \mu_c &= \text{ fixed fraction of $\mu_{t,0}$ independent with time
    [Pa$\cdot$s].} \nonumber
\end{align}
%
This measure allowed for laminar flow to develop in the core and yielded
results showing better qualitative agreement with those from the Polimi and
TUDelft models.

Figures \ref{fig:lofheat} and \ref{fig:loftemp} show the power output and
average core temperature increase during the unprotected loss of flow
transient in the Moltres, Polimi, and TUDelft models without decay heat
modeling. The three sets of results from Moltres correspond to $\mu_c =
\frac{1}{4} \mu_{t,0}, \frac{1}{2} \mu_{t,0}, \text{and } \frac{3}{4}
\mu_{t,0}$.
Although Moltres shows the same decreasing trend in power output, it failed to
capture the exact individual features in the reactor response. In the Polimi 
and TUDelft models, Fiorina et al. \cite{fiorina_modelling_2014}
stated that after around $t=15$ s, the ``flow pattern changed in the core and
the recirculation zones started to disappear''. The pocket of hot salt leaves
the core and causes a sudden drop in the average core temperature. In Moltres,
the wider peak in the average core temperature
indicates a more gradual change in the flow pattern.
